---
title: "Art Theater Project"
author: "Jiyang Xu"
date: "2023-01-27"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Main Question: 
### - What is the business trend of the art theater since 2016 until it closes in 2019?
### - Who are the major audience of the art theater and why are they attracted by this art theater?
### - What insights and suggestions could we learn from the "former glory" and business failure of the art theater?
## Main Goal: 
### - Investigating the overall trend of business activities based on different units of time period.
### - Major consumer types of the art theater and what are the events and activities held here attract them most.
### - Some further analysis on the reasons for the close and some advice for art houses to survive.

```{r}
# Overall information
library(lubridate)
library(tidyverse)
library(readr)
library(dbplyr)
library(ggplot2)
library(vcd)
library(car)
library(lmtest)
library(DescTools)
library(cowplot)

# a. ticket_sales_by_showing.txt
file.info("ticket_sales_by_showing.txt")$size
ticket_sales_origin <- read.csv("ticket_sales_by_showing.txt")
ticket_sales_origin <- na.omit(ticket_sales_origin)
view(ticket_sales_origin)

# b. gross_revenue_by_event.txt
file.info("gross_revenue_by_event.txt")$size
gross_revenue <- read.csv("gross_revenue_by_event.txt")
view(gross_revenue)
```

## 1. Showing Trend of Active Business and Audience Group
### Part I: Which are the most common and popular consumer types for the art theater?
### *Clarification: the definiation of "popular" here is P(type) > 0.05.

```{r}
type_list <- list(ticket_sales_origin %>% group_by(TicketType) %>% count())
prob_data <- data.frame(ticket_sales_origin %>% group_by(TicketType) %>% 
                          summarise(Percentage=n()/nrow(.)))
prob_data <- prob_data[order(prob_data$Percentage, decreasing = TRUE), ]
others <- sum(prob_data$Percentage[prob_data$Percentage < 0.05])
prob_data <- prob_data[prob_data$Percentage >= 0.05,]
prob_data[nrow(prob_data)+1,] <- c("Others", others)
prob_data$Percentage <- round(100*as.numeric(prob_data$Percentage), digits = 4)
prob_data

pie(prob_data$Percentage,
    labels = paste(prob_data$TicketType, sep = " ",prob_data$Percentage, "%"), 
    col = rainbow(nrow(prob_data)),
    main = "Most Popular Ticket Types in Art Theater")
```
###Conclusion: Top 3 consumer types are "Adult", "Senior Citizen", and "Student"

### Part II: Which period of time does the art theater have the most active business?
### *Clarification: the reason choosing "quantity" instead of "price" is because the per ticket price is not the same for different ticket type. Instead of caring about the overall revenue, we focus more on the overall popularity (sales) of each unit of time period. 
### - a. Overall sales trend of sales from 2016 to 2019
```{r}
# Formatting time variable: eg: "Mar 16, 2018 5:00:00 PM"
ticket_sales_origin$EventDate <- parse_date_time(ticket_sales_origin$EventDate,'%m/%d/%Y %H:%M:%S/%p')
ticket_sales_origin$Quantity <- as.numeric(ticket_sales_origin$Quantity)

ticket_sales_origin$EventDate[1] # checking whether formatting successfully or not
time1 <- ticket_sales_origin %>% 
  mutate(Year = year(EventDate))%>%
  mutate(Month = month(EventDate))%>%
  mutate(Quarter = quarter(EventDate))
time1$Quarter <- as.character(time1$Quarter)
time1 <- time1 %>% mutate(YQ = paste(Year,"Q", Quarter)) %>% mutate(YM = paste(Year, Month, seq = "_"))
time1$YQ[1] # checking whether formatting successfully or not
#time1 <- time1 %>% mutate(Quarter = paste(year1,"Q",ceiling(as.numeric(time1$month1) / 3)))

time1 <- time1[!is.na(time1$YQ),] 
ticket_sales_origin$Quantity[1] # checking the original data
time2 <- time1 %>% group_by(YQ) %>% drop_na() %>% summarise(sum_sales_q = sum(Quantity))
time3 <- time1 %>% group_by(YM) %>% drop_na() %>% summarise(sum_sales_m = sum(Quantity))

dfyear = time1 %>% group_by(Year) %>% drop_na()%>% summarise(max_month = max(Quarter), min_month = min(Quarter), avg_qtt = mean(Quantity), sum_qtt = sum(Quantity))

options(repr.plot.width=30, repr.plot.height=10)
ggplot(dfyear, aes(x = Year, y = sum_qtt)) + geom_point() + geom_path()
```

### Conculsion: Based on this line chart, 2017 and 2018 are the most active years, and further investigation is conducted later.

### - b. Overall sales trend for each quarter 
```{r}
Quarter <- c('2016Q2', '2016Q3','2016Q4','2017Q1','2017Q2','2017Q3','2017Q4','2018Q1','2018Q2','2018Q3','2018Q4','2019Q1','2019Q2','2019Q3')
#time2 <- time2[!(row.names(time2$YQ) %in% c("2016 Q 2")),]
TicketSales <- time2$sum_sales_q
df1 <- data.frame( Quarter = Quarter, TicketSales = TicketSales)
ggplot(data = df1, mapping = aes(x = factor(Quarter), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Quarter") + ylab("Total Ticket Sales") + 
  ggtitle("Quarterly Ticket Sales from 2016 to 2019")+
  theme(axis.title = element_text(size = 15, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
```

### Conclusion: Based on this trend plot, we can observed that 2018 Q3, 2017 Q1, 2018 Q2, and 2017 Q4 have the highest ticket sales here.

### - c. Overall sales trends of 2017 and 2018 by months, and the four most active quarters
```{r}
Month <- c('Jan', 'Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')
Q1 <- c('Jan', 'Feb','Mar')
Q2 <- c('Apr','May','Jun')
Q3 <- c('Jul','Aug','Sep')
Q4 <- c('Oct','Nov','Dec')

time4 <- time3[grepl("2017", time3$YM),] # 2017
time5 <- time3[grepl("2018", time3$YM),] # 2018
time6 <- time3[grepl("2017 1 _", time3$YM) | grepl("2017 2 _", time3$YM) | grepl("2017 3 _", time3$YM),] # 2017 Q1
time7 <- time3[grepl("2018 7 _", time3$YM) | grepl("2018 8 _", time3$YM) | grepl("2018 9 _", time3$YM),] # 2018 Q3
time8 <- time3[grepl("2017 10 _", time3$YM) | grepl("2017 11 _", time3$YM) | grepl("2017 12 _", time3$YM),] # 2017 Q4
time9 <- time3[grepl("2018 4 _", time3$YM) | grepl("2018 5 _", time3$YM) | grepl("2018 6 _", time3$YM),] # 2018 Q2

df_2017 <- data.frame(Month = Month, TicketSales = time4$sum_sales_m)
plot_2017 <- ggplot(data = df_2017, mapping = aes(x = factor(Month), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Month") + ylab("Total Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

df_2018 <- data.frame( Month = Month, TicketSales = time5$sum_sales_m)
plot_2018 <- ggplot(data = df_2018, mapping = aes(x = factor(Month), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Month") + ylab("Total Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

df_2017_q1 <- data.frame(Month = Q1, TicketSales = time6$sum_sales_m)
plot_2017_q1 <- ggplot(data = df_2017_q1, mapping = aes(x = factor(Q1), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Quarter 1") + ylab("Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

df_2018_q3 <- data.frame(Month = Q3, TicketSales = time7$sum_sales_m)
plot_2018_q3 <- ggplot(data = df_2018_q3, mapping = aes(x = factor(Q3), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Quarter 3") + ylab("Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

df_2017_q4 <- data.frame(Month = Q4, TicketSales = time8$sum_sales_m)
plot_2017_q4 <- ggplot(data = df_2017_q4, mapping = aes(x = factor(Q4), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Quarter 4") + ylab("Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

df_2018_q2 <- data.frame(Month = Q2, TicketSales = time9$sum_sales_m)
plot_2018_q2 <- ggplot(data = df_2018_q2, mapping = aes(x = factor(Q2), y = TicketSales, group = 1)) + 
  geom_line(colour="orange",size = 1) + 
  geom_point(colour="navy") +
  xlab("Quarter 2") + ylab("Ticket Sales") +
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))

plot_grid(plot_2017, plot_2018,
          labels = c("2017", "2018"),
          label_size = 13,
          hjust = -1,
          vjust = 1,
          nrow = 2)

plot_grid(plot_2018_q3, plot_2017_q1, plot_2018_q2, plot_2017_q4,
          labels = c("2018 Q3", "2017 Q1", "2018 Q2", "2017 Q4"),
          label_size = 8,
          hjust = -1.5,
          ncol = 2, nrow = 2)
```

## 2. Investigating Major Audience Group Within Different Events
### Part I: Processing Data Sets
### *Clarification: Since we are only interest in the specific events for major consumer types, so I choose the top three audience types (Adults, Senior Citizen, Students) and their records in quarter three in 2018 and quarter one in 2017 to represent the overall choice made by these three groups in 2017 and 2018 due to the consideration in cost savings and convenience. 

### - a. data frame for 2017 Q1
```{r}
ticket_sale_2017Q1 <- time1[grepl("2017 Q 1", time1$YQ) & (ticket_sales_$TicketType == "Adult" | ticket_sales_$TicketType == "Senior Citizen" | ticket_sales_$TicketType == "Student"),]
ticket_sale_2017Q1 <- ticket_sale_2017Q1[,c(-1,-3,-4,-7,-8,-9,-10,-11,-12,-13)]
#ticket_sale_2017Q1 <- with(ticket_sale_2017Q1, aggregate(list(Quantity = Quantity), list(EventName = EventName, TicketType = TicketType), sum))
ticket_sale_2017Q1
```

### - b. data frame for 2018 Q3
```{r}
ticket_sale_2018Q3 <- time1[grepl("2018 Q 3", time1$YQ) & (ticket_sales_$TicketType == "Adult" | ticket_sales_$TicketType == "Senior Citizen" | ticket_sales_$TicketType == "Student"),]
ticket_sale_2018Q3 <- ticket_sale_2018Q3[,c(-1,-3,-4,-7,-8,-9,-10,-11,-12,-13)]
#ticket_sale_2018Q3 <- with(ticket_sale_2018Q3, aggregate(list(Quantity = Quantity), list(EventName = EventName, TicketType = TicketType), sum))
ticket_sale_2018Q3
```
### *Clarification: 
### 1. Why is filtering the data set? Based on the table above, we can see that there are some events that have a significantly low number of records, which is likely to lead to some bias in our results. Therefore, I decide to investigate only on the ones that have records higher than 300 (roughly 100 for each audience group). 
### 2. Why is filtering the records based on the sum of each event neglecting the audience group? Since we focus more on the variation of the ticket sales between different consumer groups, it would be better to estimate it without restricting the ticket sales for groups.  

### - c. Filtering out the events with relatively more complete records, # sum of ticket sales >= 300
```{r}
ticket_sale_2017Q1_ <- with(ticket_sale_2017Q1, aggregate(list(Quantity = Quantity), list(EventName = EventName), sum))
# ticket_sale_2017Q1_ <- ticket_sale_2017Q1_ %>% filter(Quantity >= 300)
ticket_sale_2017Q1_ <- ticket_sale_2017Q1_[order(ticket_sale_2017Q1_$Quantity, decreasing = TRUE),]
ticket_sale_2017Q1_

ticket_sale_2018Q3_ <- with(ticket_sale_2018Q3, aggregate(list(Quantity = Quantity), list(EventName = EventName), sum))
# ticket_sale_2018Q3_ <- ticket_sale_2018Q3_ %>% filter(Quantity >= 300)
ticket_sale_2018Q3_ <- ticket_sale_2018Q3_[order(ticket_sale_2018Q3_$Quantity, decreasing = TRUE),]
ticket_sale_2018Q3_
```
### It is interesting to observed that the number of events in 2017 after filtering process is actually higher than the one in 2018, which means events in 2018 have higher individual sales for several specific events.
### Some thought: Even though it seems like the art theater is most active, business activity reaches its peak, but it is truly because of the specific event instead of the art theater itself attracting more audience in late 2018. After this short peak in the third quarter of 2018, it started facing the operation crisis and showing a downward trend. 

### - d. Filtering out the events chosen in previous data frame of sales sum
```{r}
common_2017 <- intersect(ticket_sale_2017Q1$EventName, ticket_sale_2017Q1_$EventName)  
ticket_sale_2017Q1 <- ticket_sale_2017Q1[ticket_sale_2017Q1$EventName %in% common_2017,]
ticket_sale_2017Q1

common_2018 <- intersect(ticket_sale_2018Q3$EventName, ticket_sale_2018Q3_$EventName)  
ticket_sale_2018Q3 <- ticket_sale_2018Q3[ticket_sale_2018Q3$EventName %in% common_2018,]
ticket_sale_2018Q3

ticket_sale_2017Q1$EventName <- as.factor(ticket_sale_2017Q1$EventName)
ticket_sale_2017Q1$TicketType <- as.factor(ticket_sale_2017Q1$TicketType)
ticket_sale_2018Q3$EventName <- as.factor(ticket_sale_2018Q3$EventName)
ticket_sale_2018Q3$TicketType <- as.factor(ticket_sale_2018Q3$TicketType)
```

###  - e. Filtering out the events chosen in gross revenue data set
```{r}
gross_revenue_2017 <- gross_revenue[gross_revenue$Event %in% common_2017,]
gross_revenue_2017 <- gross_revenue_2017[order(gross_revenue_2017$Gross.Revenue, decreasing = TRUE),]
gross_revenue_2017
gross_revenue_2018 <- gross_revenue[gross_revenue$Event %in% common_2018,]
gross_revenue_2018 <- gross_revenue_2018[order(gross_revenue_2018$Gross.Revenue, decreasing = TRUE),]
gross_revenue_2018
```

### Part II: 10 * 3 Table & Mosaic Plot & Two-Way Anova
### - a. First using mosaic plot to show the rough distribution
### *Clarification: Since it is hard to see the full name of events in the plot, so I use the first letter
```{r}
t2017_Q1 <- xtabs(Quantity ~ EventName + TicketType, data = ticket_sale_2017Q1)
t2017_Q1 

ticket_sale_2017Q1_temp = ticket_sale_2017Q1
levels(ticket_sale_2017Q1_temp$EventName) <- c("A", "B", "I", "J", "K", "L", "M", "P", "TA", "TL")
levels(ticket_sale_2017Q1_temp$TicketType) <- c("A", "SC", "SDT")
btable <- xtabs(Quantity ~ TicketType+EventName, data = ticket_sale_2017Q1_temp)
mosaic(t(btable), spacing = spacing_increase(start = 0.1, rate = 0.3), shade = TRUE) 
```

```{r}
t2018_Q3 <- xtabs(Quantity ~ EventName + TicketType, data = ticket_sale_2018Q3)
t2018_Q3

ticket_sale_2018Q3_temp = ticket_sale_2018Q3
levels(ticket_sale_2018Q3_temp$EventName) <- c("B", "S", "TW", "TIS", "W")
levels(ticket_sale_2018Q3_temp$TicketType) <- c("A", "SC", "SDT")
btable <- xtabs(Quantity ~ TicketType+EventName, data = ticket_sale_2018Q3_temp)
mosaic(t(btable), spacing = spacing_increase(start = 0.1, rate = 0.3), shade = TRUE)
```
### Conclusion: Based on the mosaic plot for 2017Q1 and 2018Q3 above, student group in "Jackie", senior citizen group in "Jakie", senior citizen group in "I Am Not Your Negro" etc. are likely to be statistically significant, and further hypothesis tests are conducted to test for our assumptions.

# - b. Two-Way Anova
```{r}
# EventName in 2017 Q1
boxplot(Quantity~EventName, data = ticket_sale_2017Q1_temp, outline=FALSE)
stripchart(Quantity~EventName, data=ticket_sale_2017Q1_temp, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
### Conclusion: Based on this plot, we find that "Jackie" has mean significantly higher than others, while others are about the same. However, we cannot tell whether there is a statistically difference here since there are boxes overlap here.

```{r}
# TicketType in 2017 Q1
boxplot(Quantity~TicketType, data = ticket_sale_2017Q1_temp, outline=FALSE)
stripchart(Quantity~TicketType, data=ticket_sale_2017Q1_temp, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
### Conclusion: Based on this plot, we find that quantity at adult group is the highest and student group is the lowest. However, we cannot tell whether there is a statistically difference here since there are boxes overlap here.

```{r}
# construct the interaction plots in 2017 Q1
interaction.plot(ticket_sale_2017Q1$TicketType, ticket_sale_2017Q1$EventName, ticket_sale_2017Q1$Quantity)
interaction.plot(ticket_sale_2017Q1_temp$EventName, ticket_sale_2017Q1$TicketType, ticket_sale_2017Q1$Quantity)
```
### Conclusion: There are intercetions in both plot.

```{r}
# EventName in 2018 Q3
boxplot(Quantity~EventName, data = ticket_sale_2018Q3_temp, outline=FALSE)
stripchart(Quantity~EventName, data=ticket_sale_2018Q3_temp, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
### Conclusion:

```{r}
# TicketType in 2018 Q3
boxplot(Quantity~TicketType, data = ticket_sale_2018Q3_temp, outline=FALSE)
stripchart(Quantity~TicketType, data=ticket_sale_2018Q3_temp, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
### Conclusion:

```{r}
# construct the interaction plots in 2018 Q3
interaction.plot(ticket_sale_2018Q3$TicketType, ticket_sale_2018Q3$EventName, ticket_sale_2018Q3$Quantity)
interaction.plot(ticket_sale_2018Q3_temp$EventName, ticket_sale_2018Q3$TicketType, ticket_sale_2018Q3_temp$Quantity)
```
### Conclusion:

## Part III: Linear Models
### - a. Fitting and Testing Linear Models
### - 1) 2017Q1
### *Clarification: From the summary made by the linear model, I found that there is no ticket sales record for blade runner for senior citizen audience group, so I removed the interaction term between them.
```{r}
# start with the full model with interactions for 2017 Q1
ticket_sale_full_2017Q1 = lm(Quantity ~ EventName*TicketType, data = ticket_sale_2017Q1, na.action = na.omit)
ticket_sale_full_2017Q1 <- update(ticket_sale_full_2017Q1, . ~ . - `EventNameBlade Runner`:`TicketTypeSenior Citizen`)
summary(ticket_sale_full_2017Q1)
Anova(ticket_sale_full_2017Q1, type = "III")
```
### Conclusion: The p-value of interaction here is 6.076e-13, which is statistically significant, so we don't remove it and the full model is the final model.

### - 2) 2018Q3
```{r}
# start with the full model with interactions for 2018 Q3
ticket_sale_full_2018Q3 = glm(Quantity ~ EventName+TicketType, family = poisson, data = ticket_sale_2018Q3, na.action = na.omit, )
summary(ticket_sale_full_2018Q3)
Anova(ticket_sale_full_2018Q3, type = "III")
```
### Conclusion: The p-value of interaction here is 2.260e-11, which is statistically significant, so we don't remove it and the full model is the final model.

### - b. Check Model Assumptions: Constancy of Variance & Normality
### - 1) 2017Q1
```{r}
par(mfrow=c(1,2))
plot(ticket_sale_full_2017Q1$fitted, ticket_sale_full_2017Q1$res, xlab="Fitted", ylab="Residuals")

# Checking Constancy of Variance
plot(ticket_sale_full_2017Q1, which = 1)
bptest(ticket_sale_full_2017Q1)

# Checking Normality
qqnorm(ticket_sale_full_2017Q1$res)
hist(ticket_sale_full_2017Q1$residuals)
shapiro.test(ticket_sale_full_2017Q1$residuals)
```
### Conclusion: Reject null hypothesis in both bp test and shapiro test, which indicates that the model satisfies normality and constant variance assumptions. No model transformation needed.

### - 2) 2018Q3
```{r}
par(mfrow=c(1,2))
plot(ticket_sale_full_2018Q3$fitted, ticket_sale_full_2018Q3$res, xlab="Fitted", ylab="Residuals")

# Checking Constancy of Variance
plot(ticket_sale_full_2018Q3, which = 1)
bptest(ticket_sale_full_2018Q3)

# Checking Normality
qqnorm(ticket_sale_full_2018Q3$res)
hist(ticket_sale_full_2018Q3$residuals)
shapiro.test(ticket_sale_full_2018Q3$residuals)
```
### Conclusion: Reject null hypothesis in both bp test and shapiro test, which indicates that the model satisfies normality and constant variance assumptions. No model transformation needed.

### - c. Pairwise Comparisons
### - 1) 2017Q1
```{r}
ANOVA=aov(ticket_sale_full_2017Q1)
ScheffeTest(ANOVA)
```


### - 2) 2018Q3
```{r}
ANOVA=aov(ticket_sale_full_2018Q3)
ScheffeTest(ANOVA)
```
From the Scheffe family CIs shown in the table, "The Farewell:Student-Pavarotti:Senior Citizen" with a p-value of 3.6e-16, "The Farewell:Senior Citizen-Pavarotti:Senior Citizen" with 9.3e-15, "Pavarotti:Senior Citizen-The Farewell:Adult" with 2.1e-11, "Pavarotti:Senior Citizen-Echo In The Canyon:Adult" with 9.3e-10, "Pavarotti:Senior Citizen-Ophelia:Adult" with 3.5e-09, "Echo In The Canyon:Student-Pavarotti:Senior Citizen" with 4.6e-09, "Pavarotti:Senior Citizen-Pavarotti:Member" with 5.8e-09, "Pavarotti:Senior Citizen-Pavarotti:Adult" with 9.7e-08... to Pavarotti:Senior Citizen-Maiden:Member with 0.0259.

Based on this output, by looking at the p-values, we can say that the highest quantity given the data set and background information is event "Pavarotti" with ticket type of "Senior Citizen", the second highest is event Maiden of ticket type "Member" while the lowest quantity is event "The Farewell" with ticket type "Student".

*Further investigations are shown in the presentation.