---
title: "Art Theater Project Data Visualization & Data Cleaning"
author: "Jiyang Xu"
date: "2023-01-27"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Main Question: 
### - What is the business trends of the art theater since 2016 until it closes in 2019?
### - Are the movie genres vary with concession types and audience group?
### - What insights and suggestions could we learn from the "former glory" and business failure of the art theater?
## Main Goal: 
### - Investigating the overall trend of business activities based on different units of time period.
### - Major consumer types of the art theater and what are the events, activities, and concessions sold here attract them most.
### - Some further analysis on the reasons for the close and some advice for art houses to survive.

```{r message=FALSE}
# Overall information
library(lubridate)
library(tidyverse)
library(readr)
library(dbplyr)
library(ggplot2)
library(vcd)
library(car)
library(lmtest)
library(DescTools)
library(cowplot)
library("ggrepel")

# a. ticket_sales_by_showing.txt
file.info("ticket_sales_by_showing.txt")$size
ticket_sales_origin <- read.csv("ticket_sales_by_showing.txt")
ticket_sales_origin <- na.omit(ticket_sales_origin)
#view(ticket_sales_origin)

# b. gross_revenue_by_event.txt
file.info("gross_revenue_by_event.txt")$size
gross_revenue <- read.csv("gross_revenue_by_event.txt")
#view(gross_revenue)

# c. concessions_sales.txt
file.info("concessions_sales.txt")$size
concessions_sales <- read.csv("concessions_sales.txt")
#view(concessions_sales)

# d. merchandise_sales.txt
file.info("merchandise_sales.txt")$size
merchandise_sales <- read.csv("merchandise_sales.txt")
#view(merchandise_sales)

# e. gift_card_transactions.txt
file.info("gift_card_transactions.txt")$size
gift_card_transactions <- read.csv("gift_card_transactions.txt")
#view(gift_card_transactions)
```

## 1. Showing Trend of Active Business and Audience Group
### Part I: Which are the most common and popular consumer types for the art theater?
### *Clarification: the definiation of "popular" here is P(type) > 0.05.

```{r}
type_list <- list(ticket_sales_origin %>% group_by(TicketType) %>% count())
prob_data <- data.frame(ticket_sales_origin[,c(5,6)])
head(prob_data)
# prob_data <- prob_data %>% dplyr::summarise(Quantity=sum(Quantity)) # 103419
prob_data <- prob_data %>% dplyr::group_by(TicketType) %>% dplyr::summarise(Quantity=sum(Quantity)) %>% dplyr::mutate(`n()/nrow(.)`=Quantity/103419)

prob_data <- prob_data[order(prob_data$`n()/nrow(.)`, decreasing = TRUE), ]
others <- sum(prob_data$`n()/nrow(.)`[prob_data$`n()/nrow(.)` < 0.05])
other <- sum(prob_data[(prob_data$`n()/nrow(.)` < 0.05),]$Quantity)
prob_data <- prob_data[prob_data$`n()/nrow(.)` >= 0.05,]
prob_data[nrow(prob_data)+1,] <- list("Others", other, others)
prob_data$`n()/nrow(.)` <- round(100*as.numeric(prob_data$`n()/nrow(.)`), digits = 4)
prob_data

pie(prob_data$`n()/nrow(.)`,
    labels = paste(prob_data$TicketType, sep = " ",prob_data$`n()/nrow(.)`, "%"), 
    col = c("red4", "red3", "red", "Grey", "Grey", "Grey"),
    main = "Ticket Types Proportion in Art Theater")
```
###Conclusion: Top 3 consumer types are "Adult", "Senior Citizen", and "Student"

### Part II: Which period of time does the art theater have the most active business?
### *Clarification: the reason choosing "quantity" instead of "price" is because the per ticket price is not the same for different ticket type. Instead of caring about the overall revenue, we focus more on the overall popularity (sales) of each unit of time period. 
### - a. Overall sales trend of sales from 2016 to 2019
```{r}
# Formatting time variable: eg: "Mar 16, 2018 5:00:00 PM"
ticket_sales_origin$EventDate <- parse_date_time(ticket_sales_origin$EventDate,'%m/%d/%Y %H:%M:%S/%p')
ticket_sales_origin$Quantity <- as.numeric(ticket_sales_origin$Quantity)
ticket_sales_origin$Price <- as.numeric(ticket_sales_origin$Price)
ticket_sales_origin <- ticket_sales_origin %>% arrange(EventDate)

ticket_sales_origin$EventDate[1] # checking whether formatting successfully or not
ticket_sales_origin <- ticket_sales_origin %>% 
  mutate(Year = year(EventDate))%>%
  mutate(Month = month(EventDate))%>%
  mutate(Quarter = quarter(EventDate))
ticket_sales_origin$Quarter <- as.character(ticket_sales_origin$Quarter)

ticket_sales_origin <- ticket_sales_origin %>% mutate(YQ = paste(Year,"Q", Quarter)) %>% mutate(YM = paste(Year, Month, seq = "_"))
ticket_sales_origin$YQ[1] # checking whether formatting successfully or not
#time1 <- time1 %>% mutate(Quarter = paste(year1,"Q",ceiling(as.numeric(time1$month1) / 3)))

ticket_sales_origin <- ticket_sales_origin[!is.na(ticket_sales_origin$YQ),] 
ticket_sales_origin$Quantity[1] # checking the original data
temp_df <- ticket_sales_origin
YQ_ticket_sales_origin <- temp_df %>% group_by(YQ) %>% drop_na() %>% dplyr::summarise(sum_sales_q = sum(Quantity))
YM_ticket_sales_origin <- temp_df %>% group_by(YM) %>% drop_na() %>% dplyr::summarise(sum_sales_m = sum(Quantity))

# don't know why sorting does not work for month, sort manually here
new_order <- c(4,5,6,7,1,2,3,8,12,13,14,15,16,17,18,19,9,10,11,20,24,25,26,27,28,29,30,31,21,22,23,32,33,34,35,36,37,38,39)
YM_ticket_sales_origin <- YM_ticket_sales_origin[new_order,]

# temp_df <- ticket_sales_origin
YQ_ticket_amounts_origin <- ticket_sales_origin %>% group_by(YQ) %>% drop_na() %>% dplyr::summarise(sum_amounts_q = sum(Price))
YM_ticket_amounts_origin <- ticket_sales_origin %>% group_by(YM) %>% drop_na() %>% dplyr::summarise(sum_amounts_m = sum(Price))
new_order <- c(4,5,6,7,1,2,3,8,12,13,14,15,16,17,18,19,9,10,11,20,24,25,26,27,28,29,30,31,21,22,23,32,33,34,35,36,37,38,39)
YM_ticket_amounts_origin <- YM_ticket_amounts_origin[new_order,]

YQ_ticket_sales_origin$Group <- rep(c("tickets"), 14)
YM_ticket_sales_origin$Group <- rep(c("tickets"), 39)
YQ_ticket_amounts_origin$Group <- rep(c("tickets"), 14)
YM_ticket_amounts_origin$Group <- rep(c("tickets"), 39)

dfyear1 = ticket_sales_origin %>% group_by(Year) %>% drop_na()%>% dplyr::summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(Quantity), 
                                                             sum_qtt = sum(Quantity))

dfamount1 = ticket_sales_origin %>% group_by(Year) %>% drop_na()%>% dplyr::summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(Price), 
                                                             sum_qtt = sum(Price))

dfyear1$Group <- c("tickets", "tickets", "tickets", "tickets")
dfamount1$Group <- c("tickets", "tickets", "tickets", "tickets")
dfyear1
dfamount1
```

### Conculsion: Based on this line chart, 2017 and 2018 are the most active years, and further investigation is conducted later.

```{r}
concessions_sales$Order.Date <- parse_date_time(concessions_sales$Order.Date,'%m/%d/%Y %H:%M:%S/%p')
concessions_sales %>% arrange(Order.Date)
concessions_sales$Price = as.numeric(gsub("\\$", "", concessions_sales$Price))
concessions_sales$Sales.Tax = as.numeric(gsub("\\$", "", concessions_sales$Sales.Tax))

concessions_sales <- concessions_sales %>% 
  mutate(Year = year(Order.Date))%>%
  mutate(Month = month(Order.Date))%>%
  mutate(Quarter = quarter(Order.Date))
concessions_sales$Quarter <- as.character(concessions_sales$Quarter)
concessions_sales <- concessions_sales %>% mutate(YQ = paste(Year,"Q", Quarter)) %>% mutate(YM = paste(Year, Month, seq = "_"))
head(concessions_sales)

temp <- concessions_sales
YQ_concessions_sales <- temp %>% group_by(YQ) %>% drop_na() %>% dplyr::summarise(sum_sales_q = sum(Quantity))
YM_concessions_sales <- temp %>% group_by(YM) %>% drop_na() %>% dplyr::summarise(sum_sales_m = sum(Quantity))

temp <- concessions_sales
YQ_concessions_amounts <- temp %>% group_by(YQ) %>% drop_na() %>% dplyr::summarise(sum_amounts_q = sum(as.numeric(Price)))
YM_concessions_amounts <- temp %>% group_by(YM) %>% drop_na() %>% dplyr::summarise(sum_amounts_m = sum(as.numeric(Price)))

new_order <- c(4,5,6,1,2,3,7,11,12,13,14,15,16,17,18,8,9,10,19,23,24,25,26,27,28,29,30,20,21,22,31,32,33,34,35,36,37,38)
YM_concessions_sales <- YM_concessions_sales[new_order,]
YM_concessions_amounts <- YM_concessions_amounts[new_order,]

YQ_concessions_sales$Group <- rep(c("concessions"), 13)
YM_concessions_sales$Group <- rep(c("concessions"), 38)
YQ_concessions_amounts$Group <- rep(c("concessions"), 13)
YM_concessions_amounts$Group <- rep(c("concessions"), 38)

temp <- concessions_sales
dfyear2 = temp %>% group_by(Year) %>% drop_na()%>% dplyr::summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(Quantity), 
                                                             sum_qtt = sum(Quantity))

concessions_sales$Total <- concessions_sales$Price * concessions_sales$Quantity + concessions_sales$Sales.Tax
temp <- concessions_sales
dfamount2 = temp %>% group_by(Year) %>% drop_na()%>% dplyr::summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(as.numeric(Total)), 
                                                             sum_qtt = sum(as.numeric(Total)))
dfyear2$Group <- c("concessions", "concessions", "concessions", "concessions")
dfyear2
dfamount2$Group <- c("concessions", "concessions", "concessions", "concessions")
dfamount2
```


```{r}
merchandise_sales$Order.Date <- parse_date_time(merchandise_sales$Order.Date,'%m/%d/%Y %H:%M:%S/%p')
merchandise_sales %>% arrange(Order.Date)
merchandise_sales$Price = as.numeric(gsub("\\$", "", merchandise_sales$Price))
merchandise_sales$Sales.Tax = as.numeric(gsub("\\$", "", merchandise_sales$Sales.Tax))

merchandise_sales <- merchandise_sales %>% 
  mutate(Year = year(Order.Date))%>%
  mutate(Month = month(Order.Date))%>%
  mutate(Quarter = quarter(Order.Date))
merchandise_sales$Quarter <- as.character(merchandise_sales$Quarter)
merchandise_sales <- merchandise_sales %>% mutate(YQ = paste(Year,"Q", Quarter)) %>% mutate(YM = paste(Year, Month, seq = "_"))

YQ_merchandise_sales <- merchandise_sales %>% group_by(YQ) %>% drop_na() %>% summarise(sum_sales_q = sum(Quantity))
YM_merchandise_sales <- temp %>% group_by(YM) %>% drop_na() %>% dplyr::summarise(sum_sales_m = sum(Quantity))

YQ_merchandise_sales$Group <- rep(c("merchandise"), 14)
YM_merchandise_sales$Group <- rep(c("merchandise"), 38)

temp <- merchandise_sales
YQ_merchandise_amounts <- temp %>% group_by(YQ) %>% drop_na() %>% summarise(sum_amounts_q = sum(as.numeric(Price)))
YM_merchandise_amounts <- temp %>% group_by(YM) %>% drop_na() %>% summarise(sum_amounts_m = sum(as.numeric(Price)))
YQ_merchandise_amounts$Group <- rep(c("merchandise"), 14)
YM_merchandise_amounts$Group <- rep(c("merchandise"), 38)

new_order <- c(4,5,6,7,1,2,3,8,12,13,14,15,16,17,18,19,9,10,11,20,24,25,26,27,28,29,30,31,21,22,23,32,33,34,35,36,37,38)
YM_merchandise_amounts <- YM_merchandise_amounts[new_order,]
YM_merchandise_sales <- YM_merchandise_sales[new_order,]

dfyear3 = merchandise_sales %>% group_by(Year) %>% drop_na()%>% summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(Quantity), 
                                                             sum_qtt = sum(Quantity))

merchandise_sales$Total <- merchandise_sales$Price*merchandise_sales$Quantity+merchandise_sales$Sales.Tax
temp <- merchandise_sales
dfamount3 = temp %>% group_by(Year) %>% drop_na()%>% summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(as.numeric(Price)), 
                                                             sum_qtt = sum(as.numeric(Price)))
dfyear3$Group <- c("merchandise", "merchandise", "merchandise", "merchandise")
dfyear3

dfamount3$Group <- c("merchandise", "merchandise", "merchandise", "merchandise")
dfamount3
```


```{r}
gift_card_transactions$Activity.Date <- parse_date_time(gift_card_transactions$Activity.Date,'%m/%d/%Y')
gift_card_transactions %>% arrange(Activity.Date)
gift_card_transactions <- gift_card_transactions %>% 
  mutate(Year = year(Activity.Date))%>%
  mutate(Month = month(Activity.Date))%>%
  mutate(Quarter = quarter(Activity.Date))
gift_card_transactions$Quarter <- as.character(gift_card_transactions$Quarter)
gift_card_transactions <- gift_card_transactions %>% mutate(YQ = paste(Year,"Q", Quarter)) %>% mutate(YM = paste(Year, Month, seq = "_"))
gift_card_transactions$Amount <-lapply(gift_card_transactions$Amount,gsub,pattern="$",fixed=TRUE,replacement="")
gift_card_transactions$Amount <- as.numeric(gift_card_transactions$Amount)

temp <- gift_card_transactions
YQ_giftcard_amounts <- temp %>% group_by(YQ) %>% drop_na() %>% summarise(sum_amounts_q = sum(as.numeric(Amount)))
YM_giftcard_amounts <- temp %>% group_by(YM) %>% drop_na() %>% summarise(sum_amounts_m = sum(as.numeric(Amount)))
YQ_giftcard_amounts$Group <- rep(c("giftcard"), 14)
YM_giftcard_amounts$Group <- rep(c("giftcard"), 37)

# 2018 2 missing, 
new_order <- c(4,5,6,7,1,2,3,8,12,13,14,15,16,17,18,19,9,10,11,20,24,25,26,27,28,29,30,31,32,33,34,35,36,37)
YM_giftcard_amounts <- YM_giftcard_amounts[new_order,]


dfyear4 = gift_card_transactions %>% group_by(Year) %>% drop_na()%>% summarise(max_month = max(Quarter), 
                                                             min_month = min(Quarter), 
                                                             avg_qtt = mean(Amount), 
                                                             sum_qtt = sum(Amount))
dfyear4$Group <- c("gift_card", "gift_card", "gift_card", "gift_card")
dfyear4
```

```{r}
dfyear <- rbind(dfyear1, dfyear2, dfyear3)
dfyear

options(repr.plot.width=30, repr.plot.height=10)
ggplot(dfyear, aes(x = Year, y = sum_qtt, group=Group)) + geom_point() + geom_line(aes(color=Group))+
  coord_cartesian(ylim = c(100, 40000))+
  ggtitle("Yearly Sales Trend from 2016 to 2019")+xlab("Year") + ylab("Sales")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  geom_point(colour="grey4", size=3)+
  geom_text(aes(label=sum_qtt), position=position_dodge(width=0.9), vjust=-0.5)
```


```{r}
dfamount <- rbind(dfamount1, dfamount2, dfamount3, dfyear4)
dfamount3
dfamount

library("ggrepel") 

options(repr.plot.width=30, repr.plot.height=10)
ggplot(dfamount, aes(x = Year, y = sum_qtt, group=Group)) + geom_point() + geom_line(aes(color=Group))+
  coord_cartesian(ylim = c(1500, 280000))+
  ggtitle("Yearly Gross Profit Trend from 2016 to 2019")+xlab("Year") + ylab("Sales")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  geom_point(colour="grey4", size=3)+
  geom_text_repel(aes(label=sum_qtt), position=position_dodge(width=0.9))
```
```{r}
dfamount <- rbind(dfamount3, dfyear4)

library("ggrepel") 

options(repr.plot.width=30, repr.plot.height=10)
ggplot(dfamount, aes(x = Year, y = sum_qtt, group=Group)) + geom_point() + geom_line(aes(color=Group))+
  coord_cartesian(ylim = c(1000, 4000))+
  ggtitle("Yearly Gross Profit Trend from 2016 to 2019")+xlab("Year") + ylab("Gross Profit")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  geom_point(colour="grey4", size=3)+
  geom_text_repel(aes(label=sum_qtt), position=position_dodge(width=0.9))
```


### - b. Overall sales trend for each quarter 
```{r}
# Quarter <- c('16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3')

#time2 <- time2[!(row.names(time2$YQ) %in% c("2016 Q 2")),]
TicketSales <- YM_ticket_sales_origin$sum_sales_m
df1 <- rbind(YM_ticket_sales_origin, YM_concessions_sales, YM_merchandise_sales)

df1$YM <- c(1:39, 2:39, 2:39)

#df1 <- data.frame( Quarter = Quarter, TicketSales = TicketSales)
ggplot(data = df1, aes(x= YM, y = sum_sales_m, group = Group)) +
  geom_line(aes(color=Group)) +
  geom_point(colour="grey4", size=1) +
  coord_cartesian(ylim = c(100, 4500)) +
  xlab("Month") + ylab("Sales") + 
  ggtitle("Monthly Sales Trend from 2016 to 2019")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  scale_x_continuous(breaks = c(2,5,8,11,14,17,20,23,26,29,32,35,38), labels = c('16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3'))
#  geom_text_repel(aes(label=sum_sales_q), position=position_dodge(width=0.3), vjust=-0.5)
```

```{r}
# Quarter <- c('16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3')
#time2 <- time2[!(row.names(time2$YQ) %in% c("2016 Q 2")),]
# TicketAmounts <- YQ_ticket_amounts_origin$sum_amounts_q


df2 <- rbind(YM_ticket_amounts_origin, YM_concessions_amounts, YM_merchandise_amounts, YM_giftcard_amounts)

df2$YM <- c(1:39, 2:39, 1:38, 1:20, 22:28, 32:38) # 2018 Feb, and 2018 Sep~Dec missing for gift card data set


#df1 <- data.frame( Quarter = Quarter, TicketSales = TicketSales)
ggplot(data = df2, mapping = aes(x = factor(YM), y = sum_amounts_m, group = Group)) +
  geom_line(aes(color=Group)) +
  geom_point(colour="grey4", size=1) +
  coord_cartesian(ylim = c(100, 37500)) +
  xlab("Month") + ylab("Gross Profit") + 
  ggtitle("Monthly Gross Profit Trend from 2016 to 2019")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  scale_x_discrete(breaks = c(2,5,8,11,14,17,20,23,26,29,32,35,38), labels = c('16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3'))
 # geom_text_repel(aes(label=sum_amounts_q[c(4,9,10,17,20,23)]), 
 #                 position=position_dodge(width=0.3), vjust=-0.5)
```
```{r}
dfamount <- rbind(YM_merchandise_amounts, YM_giftcard_amounts)

dfamount$YM <- c(1:38, 1:20, 22:28, 32:38)

# Quarter <- c('16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3',
#              '16Q2', '16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3')

options(repr.plot.width=30, repr.plot.height=10)
ggplot(dfamount, aes(x = YM, y = sum_amounts_m, group=Group))+geom_line(aes(color=Group))+
  coord_cartesian(ylim = c(10, 2000))+
  ggtitle("Monthly Gross Profit Trend from 2016 to 2019")+xlab("Monthly") + ylab("Gross Profit")+
  theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
  theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 15))+
  geom_point(colour="grey4", size=1)+
  scale_x_continuous(breaks = c(2,5,8,11,14,17,20,23,26,29,32,35,38), labels = c('16Q3','16Q4','17Q1','17Q2','17Q3','17Q4','18Q1','18Q2','18Q3','18Q4','19Q1','19Q2','19Q3'))
  # geom_text_repel(aes(label=sum_amounts_q), position=position_dodge(width=0.9))
```


### Conclusion: Based on this trend plot, we can observed that 2018 Q3, 2017 Q1, 2018 Q2, and 2017 Q4 have the highest ticket sales here.

### - c. Overall sales trends of 2017 and 2018 by months, and the four most active quarters
```{r}
# Month <- c('Jan', 'Feb','Mar','Apr','May','Jun','Jul','Aug','Sep','Oct','Nov','Dec')
# Q1 <- c('Jan', 'Feb','Mar')
# Q2 <- c('Apr','May','Jun')
# Q3 <- c('Jul','Aug','Sep')
# Q4 <- c('Oct','Nov','Dec')
# 
# time4 <- time3[grepl("2017", time3$YM),] # 2017
# time5 <- time3[grepl("2018", time3$YM),] # 2018
# time6 <- time3[grepl("2017 1 _", time3$YM) | grepl("2017 2 _", time3$YM) | grepl("2017 3 _", time3$YM),] # 2017 Q1
# time7 <- time3[grepl("2018 7 _", time3$YM) | grepl("2018 8 _", time3$YM) | grepl("2018 9 _", time3$YM),] # 2018 Q3
# time8 <- time3[grepl("2017 10 _", time3$YM) | grepl("2017 11 _", time3$YM) | grepl("2017 12 _", time3$YM),] # 2017 Q4
# time9 <- time3[grepl("2018 4 _", time3$YM) | grepl("2018 5 _", time3$YM) | grepl("2018 6 _", time3$YM),] # 2018 Q2
# 
# df_2017 <- data.frame(Month = Month, TicketSales = time4$sum_sales_m)
# plot_2017 <- ggplot(data = df_2017, mapping = aes(x = factor(Month), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Month") + ylab("Total Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# df_2018 <- data.frame( Month = Month, TicketSales = time5$sum_sales_m)
# plot_2018 <- ggplot(data = df_2018, mapping = aes(x = factor(Month), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Month") + ylab("Total Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# df_2017_q1 <- data.frame(Month = Q1, TicketSales = time6$sum_sales_m)
# plot_2017_q1 <- ggplot(data = df_2017_q1, mapping = aes(x = factor(Q1), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Quarter 1") + ylab("Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# df_2018_q3 <- data.frame(Month = Q3, TicketSales = time7$sum_sales_m)
# plot_2018_q3 <- ggplot(data = df_2018_q3, mapping = aes(x = factor(Q3), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Quarter 3") + ylab("Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# df_2017_q4 <- data.frame(Month = Q4, TicketSales = time8$sum_sales_m)
# plot_2017_q4 <- ggplot(data = df_2017_q4, mapping = aes(x = factor(Q4), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Quarter 4") + ylab("Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# df_2018_q2 <- data.frame(Month = Q2, TicketSales = time9$sum_sales_m)
# plot_2018_q2 <- ggplot(data = df_2018_q2, mapping = aes(x = factor(Q2), y = TicketSales, group = 1)) + 
#   geom_line(colour="orange",size = 1) + 
#   geom_point(colour="navy") +
#   xlab("Quarter 2") + ylab("Ticket Sales") +
#   theme(axis.title = element_text(size = 12, vjust = 0.5, hjust = 0.5))+
#   theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 20))
# 
# plot_grid(plot_2017, plot_2018,
#           labels = c("2017", "2018"),
#           label_size = 13,
#           hjust = -1,
#           vjust = 1,
#           nrow = 2)
# 
# plot_grid(plot_2018_q3, plot_2017_q1, plot_2018_q2, plot_2017_q4,
#           labels = c("2018 Q3", "2017 Q1", "2018 Q2", "2017 Q4"),
#           label_size = 8,
#           hjust = -1.5,
#           ncol = 2, nrow = 2)
```

## 2. Investigating Major Audience Group Within Different Events
### Part I: Processing Data Sets
### *Clarification: Since we are only interest in the specific events for major consumer types, so I choose the top three audience types (Adults, Senior Citizen, Students) and their records in quarter three in 2018 and quarter one in 2017 to represent the overall choice made by these three groups in 2017 and 2018 due to the consideration in cost savings and convenience. 

```{r, warning=F}
# concession sales
concessions_sales <- concessions_sales[,c(1,5,9,16,18)]
concessions_sales <- concessions_sales %>% 
  mutate(Quantity = as.numeric(Quantity)) %>% 
  pivot_wider(names_from = Product.Group, values_from = Quantity)

concessions_sales$`Non-Alcoholic Beverages` <- lapply(concessions_sales$`Non-Alcoholic Beverages`, function(x) sum(x))
concessions_sales$Candy <- lapply(concessions_sales$Candy, function(x) sum(x))
concessions_sales$Popcorn <- lapply(concessions_sales$Popcorn, function(x) sum(x))
concessions_sales$Booze <- lapply(concessions_sales$Booze, function(x) sum(x))
concessions_sales$`Baked Goods` <- lapply(concessions_sales$`Baked Goods`, function(x) sum(x))
concessions_sales$Promotions <- lapply(concessions_sales$Promotions, function(x) sum(x))

concessions_sales[,-c(1,2)] <- lapply(concessions_sales[,-c(1,2)], function(x) as.numeric(x))

# detach("package:plyr", unload=TRUE)
concessions_sales$Order.Date <- round_date(concessions_sales$Order.Date, unit = "30 mins")
concessions_sales <- lapply(concessions_sales[,-c(1,2)], function(x) aggregate(x, by=list(Order.Date=concessions_sales$Order.Date, YQ=concessions_sales$YQ), FUN=sum))

Order.Date <- concessions_sales$Total$Order.Date
YQ <- concessions_sales$Total$YQ
Total <- concessions_sales$Total$x
Candy <- concessions_sales$Candy$x
`Non-Alcoholic Beverages` <- concessions_sales$`Non-Alcoholic Beverages`$x
Popcorn <- concessions_sales$Popcorn$x
Booze <- concessions_sales$Booze$x
`Baked Goods` <- concessions_sales$`Baked Goods`$x
Promotions <- concessions_sales$Promotions$x

concessions_sales <- data_frame(Order.Date, YQ, Candy, `Non-Alcoholic Beverages`, Popcorn, Booze, `Baked Goods`, Promotions)
head(concessions_sales,10)
```

```{r, warning=F}
# ticket sales
ticket_sales <- ticket_sales_origin[,c(2,4,5,6,8,12)]
ticket_sales$TicketType[ticket_sales$TicketType!="Adult" & ticket_sales$TicketType!="Senior Citizen" & ticket_sales$TicketType!="Student"] <- "Other"

ticket_sales <- ticket_sales %>% 
  mutate(Quantity = as.numeric(Quantity)) %>% 
  pivot_wider(names_from = TicketType, values_from = Quantity)

ticket_sales$Adult <- lapply(ticket_sales$Adult, function(x) sum(x))
ticket_sales$Other <- lapply(ticket_sales$Other, function(x) sum(x))
ticket_sales$`Senior Citizen` <- lapply(ticket_sales$`Senior Citizen`, function(x) sum(x))
ticket_sales$Student <- lapply(ticket_sales$Student, function(x) sum(x))

ticket_sales[,-c(1,2,3,4)] <- lapply(ticket_sales[,-c(1,2,3,4)], function(x) as.numeric(x))

ticket_sales <- lapply(ticket_sales[,-c(1,2,4)], function(x) aggregate(x, by=list(EventName=ticket_sales$EventName, Order.Date=ticket_sales$EventDate, YQ=ticket_sales$YQ), FUN=sum))

Order.Date <- ticket_sales$Price$Order.Date
YQ <- ticket_sales$Price$YQ
EventName <- ticket_sales$Price$EventName

Price <- ticket_sales$Price$x
Adult <- ticket_sales$Adult$x
Other <- ticket_sales$Other$x
`Senior Citizen` <- ticket_sales$`Senior Citizen`$x
Student <- ticket_sales$Student$x

ticket_sales <- data_frame(Order.Date, YQ, EventName, Adult,`Senior Citizen`, Student, Other)
head(ticket_sales,10)
```


```{r}
df <- merge(ticket_sales, concessions_sales, by=c("Order.Date","YQ"), all.x = F)

# df$Adult<-ifelse(df$Adult!=0,1,0)
# df$`Senior Citizen`<-ifelse(df$`Senior Citizen`!=0,1,0)
# df$Student<-ifelse(df$Student!=0,1,0)
# df$Other<-ifelse(df$Other!=0,1,0)
# df$Candy<-ifelse(df$Candy!=0,1,0)
# df$`Non-Alcoholic Beverages`<-ifelse(df$`Non-Alcoholic Beverages`!=0,1,0)
# df$Popcorn<-ifelse(df$Popcorn!=0,1,0)
# df$Booze<-ifelse(df$Booze!=0,1,0)
# df$`Baked Goods`<-ifelse(df$`Baked Goods`!=0,1,0)
# df$Promotions <- ifelse(df$Promotions!=0,1,0)

# df<-df[,-c(1)]

head(df)
```

```{r}
genre <- read.csv("IMDb_All_Genres_etf_clean1.csv")
genre$EventName <- genre$Movie_Title
genre <- genre[,-c(1,2,3,4,5,6,7,8,10)]
head(genre)
which(is.na(df$main_genre)) # no NA!
df <- merge(df, genre, by="EventName", all.x = F) # final data set!!!
head(df)
```

```{r}
# write.csv(df, "\\Users\\xujiyang\\Downloads\\art_theater.csv", row.names=FALSE)
```

*Further investigations are shown in the presentation.