---
title: "Art Theater Project"
author: "Jiyang Xu"
date: "2023-01-27"
output: pdf_document
---
```{r}
# Main question: How does quantity change as the categories of event and ticket type change? 
# Main goal: 
# Finding the most targeting group from four major consumer types(students, adults, members, senior citizen) for speciﬁc event based on estimating ticket type for different events that results in the highest quantity for the art theater in August 2019, which is the same as finding the combination of event and the ticket type results in the highest and lowest sales of tickets in August 2019

# 1. Processing Data ("ticket_sales_by_showing.txt" and "gross_revenue_by_event.txt")
# a. ticket_sales_by_showing.txt
# Overall information
file.info("ticket_sales_by_showing.txt")$size
ticket_sales_ <- read.csv("ticket_sales_by_showing.txt")

# Filtering data of ticket sales in Auguest 2019, the last month the theater opens
ticket_sale <- ticket_sales_[grepl("2019", ticket_sales_$EventDate) & grepl("Aug", ticket_sales_$EventDate) & (ticket_sales_$TicketType == "Member" | ticket_sales_$TicketType == "Adult" | ticket_sales_$TicketType == "Student" | ticket_sales_$TicketType == "Senior Citizen"),]
ticket_sale <- ticket_sale[,c(-1,-3,-4,-7,-8)]

# count the occurrences of different movies and drop the movies occur below 15
table(ticket_sale$EventName)
ticket_sale_ <- ticket_sale[ticket_sale$EventName == 'Echo In The Canyon' | ticket_sale$EventName == "Maiden" | ticket_sale$EventName == "Ophelia" | ticket_sale$EventName == "Pavarotti" | ticket_sale$EventName == "The Farewell",]
# Set event name, ticket type, and item price as factor parameters, quantity as the respond variable
ticket_sale_$EventName <- as.factor(ticket_sale_$EventName)
is.factor(ticket_sale_$EventName)
table(ticket_sale_$EventName) 
nlevels(ticket_sale_$EventName)
ticket_sale_$TicketType <- as.factor(ticket_sale_$TicketType)
nlevels(ticket_sale_$TicketType)
ticket_sale_
# Now the data frame of ticket sales is the data represents the events that have relatively complete records (#data total >= 15) and four different groups of people (member, adult, student, and senior citizen) in August 2019, one month before the art theater closed 

# b. gross_revenue_by_event.txt
file.info("gross_revenue_by_event.txt")$size
gross_revenue <- read.csv("gross_revenue_by_event.txt")

# Filtering data of five movies selected
gross_revenue_ <- gross_revenue[gross_revenue$Event == 'Echo In The Canyon' | gross_revenue$Event == "Maiden" | gross_revenue$Event == "Ophelia" | gross_revenue$Event == "Pavarotti" | gross_revenue$Event == "The Farewell",]
gross_revenue_
# Now the data frame of gross revenue is the data represents the events that have relatively complete records (#data total >= 15) in Auguest 2019
```

```{r}
# First using mosaic plot to show the percentages of data and rough distribution of event and ticket type
library(vcd)
# hard to see the full name of events in the graph, so use the first letter
ticket_sale <- ticket_sale_
ticket_sale$TicketType <- as.factor(ticket_sale$TicketType)
ticket_sale$EventName <- as.factor(ticket_sale$EventName)
levels(ticket_sale$EventName)
levels(ticket_sale$TicketType)
levels(ticket_sale$EventName) <- c("E", "M", "O", "P", "F")
levels(ticket_sale$TicketType) <- c("A", "M", "SS", "SDT")
btable <- xtabs(Quantity ~ TicketType+EventName, data = ticket_sale)
btable
mosaic(t(btable), spacing = spacing_increase(start = 0.5, rate = 0.6), shade = TRUE)
```
Based on the mosaic plot above, senior citizen group in "Echo In The Canyon", senior citizen group in "Pavarotti", "The Farewell" in adult and member groups are significant here, and further hypothesis tests are conducted to test for our assumptions.


```{r}
# 2. Two-Way Anova
boxplot(Quantity~EventName, data = ticket_sale_, outline=FALSE)
stripchart(Quantity~EventName, data=ticket_sale_, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
Based on this plot, we find that five events are at the same level except ophelia and we cannot tell whether there is a statistically difference here.

```{r}
boxplot(Quantity~TicketType, data = ticket_sale_, outline=FALSE)
stripchart(Quantity~TicketType, data=ticket_sale_, method="jitter", col="blue", vertical=TRUE, add=TRUE)
```
Based on this plot, we find that quantity at all four levels are at different level but adult and senior citizen, student and member have relatively same level. However, we cannot tell whether there is a statistically difference here since there are boxes overlap here.

```{r}
# construct the interaction plots
interaction.plot(ticket_sale_$TicketType, ticket_sale_$EventName, ticket_sale_$Quantity)
interaction.plot(ticket_sale_$EventName, ticket_sale_$TicketType, ticket_sale_$Quantity)
```
There are intercetions in both groups

```{r}
# Investigate whether the interactions are statistically significant or not
# start with the model with interactions
library(car)
ticket_sale_full = lm(Quantity ~ EventName*TicketType, data = ticket_sale_)
summary(ticket_sale_full)
Anova(lm(Quantity ~ EventName*TicketType, data = ticket_sale_), type = "III")
```
The p-value of interaction here is 6.076e-13, which is statistically significant, so we don't remove it and the full model is the final model.

```{r}
# 3. Check Model Assumption
par(mfrow=c(1,2))
plot(ticket_sale_full$fitted, ticket_sale_full$res, xlab="Fitted", ylab="Residuals")

# Checking Constancy of Variance
plot(ticket_sale_full, which = 1)
library(lmtest)
bptest(ticket_sale_full)

# Checking Normality
qqnorm(ticket_sale_full$res)
hist(ticket_sale_full$residuals)
shapiro.test(ticket_sale_full$residuals)
```
Reject null hypothesis in both bp test and shapiro test, which indicates that the model satisfies normality and constant variance assumptions. No model transformation needed.

```{r}
# 4. Pairwise Comparisons
library(DescTools)
ANOVA=aov(ticket_sale_full)
ScheffeTest(ANOVA)
```
From the Scheffe family CIs shown in the table, "The Farewell:Student-Pavarotti:Senior Citizen" with a p-value of 3.6e-16, "The Farewell:Senior Citizen-Pavarotti:Senior Citizen" with 9.3e-15, "Pavarotti:Senior Citizen-The Farewell:Adult" with 2.1e-11, "Pavarotti:Senior Citizen-Echo In The Canyon:Adult" with 9.3e-10, "Pavarotti:Senior Citizen-Ophelia:Adult" with 3.5e-09, "Echo In The Canyon:Student-Pavarotti:Senior Citizen" with 4.6e-09, "Pavarotti:Senior Citizen-Pavarotti:Member" with 5.8e-09, "Pavarotti:Senior Citizen-Pavarotti:Adult" with 9.7e-08... to Pavarotti:Senior Citizen-Maiden:Member with 0.0259.

Based on this output, by looking at the p-values, we can say that the highest quantity given the data set and background information is event "Pavarotti" with ticket type of "Senior Citizen", the second highest is event Maiden of ticket type "Member" while the lowest quantity is event "The Farewell" with ticket type "Student".

*Further investigations are shown in the presentation.